The problem and promise of scale in multilayer networks

### 2020-01-28 paper/manuscript.Rmd
fst metric interpretation summary

>>>>

### Each metric's interpretation
* Multidegree: sum of degree across layers. High multidegree = connected to many individuals across layers. Low multidegree = not connected to many individuals across layers. 
* Degree deviation: deviation of degree across layers. High degree deviation = large difference between degree for an individual across layers. Low degree deviation = individuals are similarly connected across layers. 
*

###
